\large{\bf Large effects and the infinitesimal model }

### 2023-12-05 writeup.tex
minor fixen

In summary, the limiting effect of the initial generation can take one of only forms:
either a constant (i.e., the initial generation only determines the mean),
or a Cauchy distribution.

>>>>

In summary, if the left- or right-hand derivative of $\psi_\infty$ exists,
then the limiting effect of the initial generation can take one of only two forms:
either a constant (i.e., the initial generation only determines the mean),
or a Cauchy distribution.
However, it is unclear if there are cases where these derivatives do not exist
and these effects converge to a meaningful limit.
